A Temporal Logic Based Framework for Intrusion Detection

### 2023-09-04 Paper/main.tex
update

The definitions of $evaluate$, $update$ and $value$ on the different primitive operators are the following:
\begin{align*}
    evaluate(\underline{\text{true}},\alpha_i) & =\ \underline{\text{true}} \\
    evaluate(\underline{\text{false}},\alpha_i) & =\ \underline{\text{false}} \\ 
    evaluate(\text{exp},\alpha_i) & =\ \text{value of } exp\text{ in } \alpha_i \\
    evaluate(F_1\ op\ F_2,\alpha_i) & =\  evaluate(F_1,\alpha_i)\ op\ evaluate(F_2,\alpha_i)\quad \text{where op can be }\lor , \land, \rightarrow \\
    evaluate(\neg{F},\alpha_i) & =\ \neg{evaluate(F,\alpha_i)}  \\
    evaluate(\bigcirc F,\alpha_i) & =\ update(F,\alpha_i)  \\
    evaluate(F_1 \cdot F_2,\alpha_i) & =
    \begin{cases}
        \text{if } value(F_1)=\ \underline{\text{false}} \\
        \quad  evaluate(F_1,\alpha_i)\cdot F_2 \\
        \text{else} \\
        \quad  evaluate(F_1,\alpha_i)\cdot F_2 \lor evaluate(F_2,\alpha_i)
    \end{cases}
\end{align*}

>>>>

According to~\cite{barringer2004rule}, the definitions of $evaluate$, $update$ and $value$ on the different primitive operators are the following ($op\text{ can be }\lor , \land, \rightarrow $):
%evaluate
\begin{align*}
    evaluate(\underline{\text{true}},\alpha_i) & =\ \underline{\text{true}} \\
    evaluate(\underline{\text{false}},\alpha_i) & =\ \underline{\text{false}} \\ 
    evaluate(\text{exp},\alpha_i) & =\ \text{value of } exp\text{ in } \alpha_i \\
    evaluate(F_1\ op\ F_2,\alpha_i) & =\  evaluate(F_1,\alpha_i)\ op\ evaluate(F_2,\alpha_i)\\
    evaluate(\neg{F},\alpha_i) & =\ \neg{evaluate(F,\alpha_i)}  \\
    evaluate(\bigcirc F,\alpha_i) & =\ update(F,\alpha_i)  \\
    evaluate(F_1 \cdot F_2,\alpha_i) & =
    \begin{cases}
        evaluate(F_1,\alpha_i)\cdot F_2 \quad \text{if } value(F_1)=\ \underline{\text{false}} \\
        evaluate(F_1,\alpha_i)\cdot F_2 \lor evaluate(F_2,\alpha_i)\quad \text{else} 
    \end{cases}\\ \\
%value
    value(\underline{\text{true}}) & =\ \underline{\text{true}} \\
    value(\underline{\text{false}}) & =\ \underline{\text{false}} \\ 
    value(\text{exp}) & =\ \underline{\text{false}} \\
    value(F_1\ op\ F_2) & =\  value(F_1)\ op\ value(F_2) \\
    value(\neg{F}) & =\ \neg{value(F)}  \\
    value(\bigcirc F) & =
    \begin{cases}
        F \quad \text{if at the beginning of a trace} \\
        \underline{\text{false}}\quad \text{if at the end of a trace} \\
    \end{cases}\\
    value(F_1 \cdot F_2,\alpha_i) & =\  value(F_1)\land value(F_2) 
\end{align*}
%update
\begin{align*}
    evaluate(\underline{\text{true}},\alpha_i) & =\ \underline{\text{true}} \\
    evaluate(\underline{\text{false}},\alpha_i) & =\ \underline{\text{false}} \\ 
    evaluate(\text{exp},\alpha_i) & =\ \text{value of } exp\text{ in } \alpha_i \\
    evaluate(F_1\ op\ F_2,\alpha_i) & =\  evaluate(F_1,\alpha_i)\ op\ evaluate(F_2,\alpha_i)\quad \text{where op can be }\lor , \land, \rightarrow \\
    evaluate(\neg{F},\alpha_i) & =\ \neg{evaluate(F,\alpha_i)}  \\
    evaluate(\bigcirc F,\alpha_i) & =\ update(F,\alpha_i)  \\
    evaluate(F_1 \cdot F_2,\alpha_i) & =
    \begin{cases}
        \text{if } value(F_1)=\ \underline{\text{false}} \\
        \quad  evaluate(F_1,\alpha_i)\cdot F_2 \\
        \text{else} \\
        \quad  evaluate(F_1,\alpha_i)\cdot F_2 \lor evaluate(F_2,\alpha_i)
    \end{cases}
\end{align*}
